---
title: "ODK Central data management"
subtitle: "Overview of the data collection infrastructure"
projectname: "PROJECTNAME"
author:
  - name: Hélène Langet
    email: helene.langet@swisstph.ch
date: last-modified
date-format: "YYYY-MM-DDTHH:mm:ssZ"
format:
  report-typst: default
TPH-icon: ./_extensions/report/images/TPHicon.jpeg
TPH-logo: ./_extensions/report/images/TPHlogo4.png
      
mainfont: Arial
fontsize: 11pt
      
execute:
  echo: false
  warning: false

params:
  svc: null
---

<!-- Load libraries -->

```{r}
library(httr)
library(dplyr)
library(flextable)
library(knitr)
library(purrr)
library(rvest)
```

{{< pagebreak >}}

# Executive summary

This report gives an overview of the **ODK Central system** set up for the **{{< meta projectname >}} project**. ODK Central is the platform used to manage and collect project data.

## For project managers and non-technical readers

The report is created directly from the system itself, which means the information you see is always **up to date** at the timestamp it is produced (**{{< meta date >}}**).

## For technical teams and developers

This report was generated automatically using **`r R.version.string`** and **Quarto `r system("quarto --version", intern = TRUE)`** to ensure reproducibility.

`{r} params$svc`

{{< pagebreak >}}

# About ODK

```{r}
security_url <- "https://docs.getodk.org/security/"
```

Security information has been directly updated from [`r security_url`](`r security_url`) on **{{< meta date >}}**. Since the servers are self-hosted, items marked with a question mark depend on the specific self-hosted configuration.

```{r}
#| tbl-cap: "ODK security considerations"
#| label: tbl-odk-security

rvest::read_html(security_url) |>
  rvest::html_element("div.table-wrapper.colwidths-given.docutils.container table") |> 
  rvest::html_table() |>
  dplyr::select(-`ODK Cloud`) |>
  knitr::kable(escape = FALSE)
```

```{r}
users_url <- "https://docs.getodk.org/central-users/"
```

ODK Central role information has been directly updated from [`r users_url`](`r users_url`) on **{{< meta date >}}**.

```{r}
#| tbl-cap: "Web user roles"
#| label: tbl-odk-webuser-roles

rvest::read_html(users_url) |>
  rvest::html_element("div.table-wrapper.docutils.container table") |> 
  rvest::html_table() |>
  knitr::kable(escape = FALSE)
```
