---
title: "ODK Central data management"
subtitle: "Overview of the data collection infrastructure"
author:
  - name:
      given: Hélène
      family: Langet
    email: helene.langet@swisstph.ch
    affiliations:
      - name: Swiss Tropical and Public Health Institute (Research Informatics)
  - name:
      given: Zhihan
      family: Zhu
    email: zhihan.zhu@swisstph.ch
    affiliations:
      - name: Swiss Tropical and Public Health Institute (Research Informatics)
  - name:
      given: Aurelio
      family: Di Pasquale
    email: aurelio.dipasquale@swisstph.ch
    affiliations:
      - name: Swiss Tropical and Public Health Institute (Research Informatics)
date: last-modified
date-format: "YYYY-MM-DDTHH:mm:ssZ"

params:
  base_url: null
  pid: null
  project_name: "Default Project"

format:
  report-typst:
    toc-title: "Table of Contents"
    toc: true
    toc-depth: 3
    number-sections: true
      
mainfont: Arial
fontsize: 11pt
      
execute:
  echo: false
  warning: false
  
projectname: "`r params$project_name`"
---

<!-- Load libraries -->

```{r}
library(httr)
library(dplyr)
library(flextable)
library(knitr)
library(purrr)
library(rvest)
library(gt)
```

{{< pagebreak >}}

# Executive summary

This report gives an overview of the **ODK Central system** set up for the **`r params$project_name` project**. ODK Central is the platform used to manage and collect project data.

**Who is this report for?** It is mainly intended for project managers and technical staff who oversee or support the data management system.

## For project managers and non-technical readers

The report is created directly from the system itself, which means the information you see is always **up to date** at the timestamp it is produced (**{{< meta date >}}**).

## For technical teams and developers

This report was generated automatically using **`r R.version.string`** and **Quarto `r system("quarto --version", intern = TRUE)`** to ensure reproducibility.

{{< pagebreak >}}

# Server configuration

## General

* ODK Central URL: [`r params$base_url`](`r params$base_url`)
* Project ID: `r params$pid`

```{r}
ruODK::ru_setup(
  svc = Sys.getenv("ODKC_SVC"),
  un = Sys.getenv("ODKC_UN"),
  pw = Sys.getenv("ODKC_PW"),
  tz = Sys.getenv("TZ"))
```

## Overview of forms and entities

This section summarizes the forms and entities currently available in the project with ID `r params$pid`.

```{r}
#| label: tbl-forms
#| tbl-cap: "List of forms"

ruODK::form_list() |>
  dplyr::select(xml_form_id,
                name,
                state,
                version,
                submissions) |> 
  gt::gt()
```

```{r}
#| label: tbl-entities
#| tbl-cap: "List of entities."

ruODK::entitylist_list() |>
  dplyr::select(-created_at,
                -project_id) |> 
  gt::gt()
```

## Access

This section describes the user access configuration for the project with ID `r params$pid`.

### Web user project managers

Project Managers can perform any administrative task related to this Project and can fill Forms out in a web browser

### Web user project viewers

Project Viewers can access and download all Form and Entity data in this Project, but cannot make any changes to settings or data.

### Web user data collectors

Data Collectors can fill Forms out in a web browser, but cannot view or change data or settings.

{{< pagebreak >}}

# About ODK

```{r}
security_url <- "https://docs.getodk.org/security/"
```

Security information has been directly updated from [`r security_url`](`r security_url`) on **{{< meta date >}}**. Since the servers are self-hosted, items marked with a question mark depend on the specific self-hosted configuration.

```{r}
#| tbl-cap: "ODK security considerations"
#| label: tbl-odk-security

rvest::read_html(security_url) |>
  rvest::html_element("div.table-wrapper.colwidths-given.docutils.container table") |> 
  rvest::html_table() |>
  dplyr::select(-`ODK Cloud`) |>
  knitr::kable(escape = FALSE)
```

```{r}
users_url <- "https://docs.getodk.org/central-users/"
```

ODK Central role information has been directly updated from [`r users_url`](`r users_url`) on **{{< meta date >}}**.

```{r}
#| tbl-cap: "Web user roles"
#| label: tbl-odk-webuser-roles

rvest::read_html(users_url) |>
  rvest::html_element("div.table-wrapper.docutils.container table") |> 
  rvest::html_table() |>
  knitr::kable(escape = FALSE)
```
