---
title: "ODK Data Export Demo"
author:
  - name:
      given: Hélène
      family: Langet
    affiliations:
      - Research Informatics
    email: helene.langet@swisstph.ch
date: last-modified
format:
  html: default
      
execute:
  echo: true
  warning: false
  error: true
---

## Overview

This document demonstrates the `odk_pipeline_utilities.R` workflow:

1. **Fetch & clean** the form schema with `odk_get_schema()`
2. **Build the export** data frame with `odk_build_export()`
3. **Write outputs** with `odk_write_stata()` and `odk_write_codebook()`

---

## Setup

```{r}
#| label: setup

library(tidyverse)
library(labelled)
library(ruODK)
library(haven)
library(codebookr)

source("../../R/odk_pipeline_utilities.R")
```

Configure your `ruODK` connection once before running any pipeline step:

```{r}
#| label: ruodk-setup

ruODK::ru_setup(
  svc = Sys.getenv("ODKC_TEST_SVC"),
  un  = Sys.getenv("ODKC_TEST_UN"),
  pw  = Sys.getenv("ODKC_TEST_PW"),
  tz = Sys.getenv("TEST_TZ"),
  verbose = FALSE
)
```

---

```{r}
form_id <- "va_who_2022"  # change to your form ID
```

## Step 1 — Fetch the form schema

`odk_get_schema()` calls `ruODK::form_schema_ext()`, renames label/choice
columns, cleans text, applies any answer replacements, and filters out
system/generated fields.

```{r}
#| label: get-schema-simple

# Single-language form: label_col and choices_col are auto-detected
schema <- odk_get_schema(fid = form_id)
```

The tibble returned by `odk_get_schema` always has exactly four columns:

| Column          | Description                                      |
|-----------------|--------------------------------------------------|
| `ruodk_name`    | Field name as stored in ODK Central              |
| `lbl`           | Human-readable label (cleaned)                   |
| `answers`       | Serialised choice map (parsed downstream)        |
| `selectMultiple`| `TRUE` for select_multiple fields                |

```{r}
#| label: get-schema-parametrised

# Multi-language form: specify the language explicitly
# Optionally add answer replacements or extra field exclusions beyond the built-in ones (e.g. exclude all fields starting with "meta_")
schema <- odk_get_schema(
  fid                    = form_id,
  label_col              = "label_english_(en)",
  choices_col            = "choices_english_(en)",
  replacements           = c("Old value" = "New value"),  # optional
  extra_exclude_patterns = "^meta_"                       # optional
)

schema |> 
  knitr::kable()
```



---

## Step 2 — Fetch raw submissions

```{r}
#| label: get-submissions

submissions <- ruODK::odata_submission_get(fid = form_id)
submissions
```

---

## Step 3 — Build the export data frame

`odk_build_export()` chains four sub-steps internally:

- **4a** Keep only schema variables
- **4b** Expand `select_multiple` columns into 0/1 dummy columns
- **4c** Map coded values to labels
- **4d** Attach variable labels (`labelled`)
- **4e** Strip form-prefix from column names (skips duplicates)

```{r}
#| label: build-export

out <- odk_build_export(
  df     = submissions,
  schema = schema,
  id_col = "id"          # default; change if your key column differs
)
export_df <- out$df1
```

### Inspecting labels

```{r}
#| label: inspect-labels

# Show variable labels for the first 10 columns
labelled::var_label(export_df) |>
  head(10) |> 
  knitr::kable()
```

---

## Step 4 — Write outputs

### Stata `.dta`

```{r}
#| label: write-stata

odk_write_stata(export_df, path = "clean_data.dta")
```

### Codebook (Word)

```{r}
#| label: write-codebook

form_title = "2022 WHO Verbal Autopsy instrument V1.1"

odk_write_codebook(
  df       = out$df2,
  schema   = schema,
  path     = "codebook.docx",
  title    = form_title
)
```

---

## Full pipeline (one block)

For production use, the entire pipeline can be run in a single chunk:

```{r}
#| label: full-pipeline

form_id = "va_who_2022"  # change to your form ID
form_title = "2022 WHO Verbal Autopsy instrument V1.1"

# 1. Schema
schema <- odk_get_schema(
  fid                    = form_id,
  label_col              = "label_english_(en)",
  choices_col            = "choices_english_(en)",
  replacements           = c("Old value" = "New value"),  # optional
  extra_exclude_patterns = "^meta_"                       # optional
)

# 2. Submissions
submissions <- ruODK::odata_submission_get(fid = form_id)

# 3. Export data frame
export_df <- odk_build_export(submissions, schema)

# 4. Outputs
odk_write_stata(export_df,    "clean_data.dta")
odk_write_codebook(export_df, "codebook.docx",
                   title    = form_title)
```
